---
title: "Reproducible_research_assignment_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Loading the packages
```{R}
library(ggplot2)
library(lubridate)
library(Hmisc)
```


##Loading and preprocessing the data

###1. Load the data(i.e. read.csv())

```{r}
if (!file.exists("activity.csv")){
    unzip("repdata%2Fdata%2Factivity.zip")
}
activity = read.csv("activity.csv")

```

###2. Process/transform the data(if necessary) into a format suitable for your analysis

```{R}
activity$date = ymd(activity$date)
```



##What is the mean total number of steps taken per day?

###1.Calculate the total number of steps taken per day and plot it in histogram by qplot
```{R}
activity$steps_per_day = tapply(activity$steps, activity$date, sum, na.rm=TRUE)
qplot(activity$steps_per_day, xlab="Steps per day", ylab = "Number")
```

###2. Calculate and report the mean and median of the total number of steps taken per day

```{R}
steps_Mean=mean(activity$steps_per_day)
steps_median=median(activity$steps_per_day)
steps_Mean
steps_median
```



##What is the average daily activity pattern?

###1. Make a time series plot

```{R}
average = aggregate(x=list(mean_steps= activity$steps), by = list(interval=activity$interval), FUN=mean, na.rm=TRUE)
ggplot(data=average, aes(x=interval, y= mean_steps))+ geom_line()+xlab("5 minutes interval")+ylab("average of steps")
```

###2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{R}
most = which.max(average$mean_steps)
time_most_steps = gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2", average[most,"interval"])
time_most_steps
```



##Imputing missing values
###1. Calculate and report the totla number of missing values in the dataset
```{R}
num_missing_value =length(which(is.na(activity$steps)))
num_missing_value
```

###2. Devise a strategy for filling in all of the missing valuers in the dataset: filling mean to NA.

###3. Create a new dataset that is equal to the original dataset but with the missing data filled in
```{R}
new_activity = activity
new_activity$steps= impute(activity$steps, fun=mean)
```

###4. Make a histogram of the total number of steps taken each day and claculate and report the mean and median total number of steps taken per day.

```{R}
new_steps_per_day = tapply(new_activity$steps,new_activity$date, sum )
qplot(new_steps_per_day, xlab = "Steps per day", ylab = "Number", main = "replace missing values to the mean of the rest")
new_steps_Mean= mean(new_steps_per_day)
new_steps_median=median(new_steps_per_day)
new_steps_Mean
new_steps_median
```

##Are there difference in activity patterns between weekdays and weekends?

###1. Create a new factor variable in the data set with two levels

```{R}
new_activity$date_type = ifelse(as.POSIXlt(new_activity$date)$wday %in% c(0,6), "weekend", "weekday")
```

###2. Make a penal plot containing a time series plot

```{R}
new_average = aggregate(steps~interval+date_type, data=new_activity, mean)
ggplot(new_average, aes(interval, steps)) + geom_line()+facet_grid(date_type~.)+ xlab("5-minute interval") + ylab("average number of steps")
```







